### 2021-02-09 manuscript.tex
Add manuscript template

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Physics Letters A}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{Multiple quantum NMR in solids as a method of a determination of Wigner-Yanase skew information}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author[icp]{S.~I.~Doronin}
\author[icp]{E.~B.~Feldman}
\author[icp,msu]{I.~D.~Lazarev}
\address[icp]{Institute of Problems of Chemical Physics of Russian Academy of Sciences, \\ Chernogolovka, Moscow Region, Russia 142432}
\address[msu]{Faculty of Fundamental Physical-Chemical Engineering, Lomonosov Moscow State University, GSP-1, Moscow, Russia 119991}

\begin{abstract}
%% Text of abstract

\end{abstract}

%%Graphical abstract
%\begin{graphicalabstract}
%\includegraphics{...}
%\end{graphicalabstract}

%%Research highlights
%\begin{highlights}
%\item Research highlight 1
%\item Research highlight 2
%\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
multiple quantum (MQ) NMR \sep 
%% PACS codes here, in the form: \PACS code \sep code
%\PACS 0000 \sep 1111
%%
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC 0000 \sep 1111
\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:1}

\section{MQ NMR for solving problems of quantum informatics}
\label{sec:2}

\section{The Wigner-Yanase skew information and MQ NNR}
\label{sec:3}

\section{A comparison of the many-spin entanglement obtained with the Wigner-Yanase information and the Fisher information}
\label{sec:4}

\section{Conclusion}
\label{sec:5}

\section{Acknowledgement}
\label{sec:6}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%\appendix
%\section{Sample Appendix Section}
%\label{sec:sample:appendix}
%Lorem ipsum dolor sit amet...

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
 \bibliographystyle{elsarticle-num} 
 \bibliography{bibliography}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

% \begin{thebibliography}{00}

% %% \bibitem{label}
% %% Text of bibliographic item

% \bibitem{}

% \end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2021-02-13 manuscript.tex
Add zerodraft

@@
 %% \usepackage{amsthm}
+%% The amsmath package provides a handful of options for displaying equations.
+\usepackage{amsmath}
 
@@
 %% for the whole article with \linenumbers.
-%% \usepackage{lineno}
+\usepackage{lineno}
 
@@
 
-\title{Multiple quantum NMR in solids as a method of a determination of Wigner-Yanase skew information}
+\title{Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information}
 
@@
 %% Text of abstract
-
+A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with the dipole-dipole interactions in MQ NMR experiments in solids.
+It is shown that the Wigner--Yanase skew information at temperature is equal to the doubled second moment of the MQ NMR spectra at the temperature twice large and any evolution times.
+A comparison of the many--spin entanglement obtained with the Wigner--Yanase information and the Fisher information is conducted.
 \end{abstract}
@@
 
-%% \linenumbers
+\linenumbers
 
 %% main text
+
 \section{Introduction}
 \label{sec:1}
+The Wigner--Yanase skew information~\cite{1,2,3} together with the Fisher information~\cite{4,5} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{6,7}.
+Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
+In particular, it was shown~\cite{6,8} that a low bound on the quantum Fisher information~\cite{4,5} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
+As a result, the low bound on the quantum Fisher information can be found in MQ NMR experiments~\cite{9},
+in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
+Using the properties of the quantum Fisher Information one can obtain a number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
+
+The Wigner--Yanase skew information~\cite{1,2,3} is also connected with the spectrum of MQ coherences.
+In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(S = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{9} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
+Using the properties of the Wigner--Yanase skew information one can investigate the many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{9}.
+
+The main aim of the present article is a development of the method of extracting the Wigner--Yanase skew information from the MQ NMR spectra.
+We also compare on the simple models~\cite{7,15} the many--spin entanglement obtained both with the Wigner--Yanase information and the Fisher information.
+
+The article is organized as follows.
+In Sec.~\ref{sec:2} the short introduction to the MQ NMR spectroscopy is given.
+The connection of the Wigner--Yanase skew information with the second moment of the MQ NMR spectrum is obtained in Sec.~\ref{sec:3}.
+A comparison of the many--spin entanglement obtained with Wigner--Yanase information and the Fisher information on the simple models~\cite{7,15} is conducted in Sec.~\ref{sec:4}.
+We briefly discuss our results in the concluding Sec.~\ref{sec:5}.
 
@@
 
-\section{The Wigner-Yanase skew information and MQ NNR}
+\begin{figure}
+	\includegraphics[width=0.95\linewidth]{mq-experiment}
+	\caption{The basic scheme of the multiple quantum NMR experiment.}
+	\label{fig:1}
+\end{figure}
+
+MQ NMR methods are widely used for solving problems of quantum informatics~\cite{16,17}.
+The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{9}.
+MQ NMR coherences are created by a periodic multipulse sequence, consisting of $I_x$-pulses, irradiating the system of the preparation period~\cite{9}.
+If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18} 
+MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$
+%
+\begin{equation} \label{eq:1}
+        H_{MQ} = H^{(+2)} + H^{(-2)} , \quad
+        H^{(\pm 2)} = -\frac{1}{2} \sum_{j<k} D_{jk} I_{j} ^\pm I_k^\pm,
+\end{equation}
+%
+where $D_{jk}$ is the coupling constant between spins $j$ and $k$, and $I_{j} ^+ I_k ^-$ are the raising and lowering operators of spin $j$.
+On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
+As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{9}.
+
+In order to investigate the MQ NMR dynamics of the system on the preparation period~\cite{9} one should find the density matrix $\rho(t)$ by solving the Liouville evolution equation~\cite{18}
+
+\begin{equation}
+    \label{eq:2}
+        i\frac{d\rho(t)}{dt} = [H_{MQ}, \rho(t)]
+\end{equation}
+with the initial thermodynamic equilibrium density matrix
+\begin{equation}
+    \label{eq:3}
+        \rho(0) = \rho_\mathrm{eq} = \frac{\exp(\frac{\hbar \omega_0}{kT}I_z)}{Z},
+\end{equation}
+where $Z=Tr \left\{e\frac{\hbar \omega_0}{kT}I_z \right\}$ is the partition function, $\hbar$ and $k$ are the Pauli and Boltzmann constants, $\omega_0$ is the Larmor frequency, $T$ is the temperature, and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis, which is directed along the strong external magnetic field.
+
+Following the preparation evolution and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{9}, the resulting signal $G(\tau,\phi)$ stored as population information is
+%
+\begin{equation} \label{eq:4}
+	\begin{split}
+		G(\tau,\phi)
+		& = Tr \left\{
+			e^{iH_{MQ}\tau} e^{i\phi I_z} e^{-iH_{MQ}\tau} \rho_\mathrm{eq}
+			e^{iH_{MQ}\tau} e^{-i\phi I_z} e^{-iH_{MQ}\tau}\rho_\mathrm{eq}
+		\right\}
+		\\
+		& = Tr \left\{
+			e^{i\phi I_z} \rho_\mathrm{pre}(\tau,\beta)
+      e^{-i\phi I_z}\rho_\mathrm{pre}(\tau,\beta)
+		\right\},
+	\end{split}
+\end{equation}
+%
+where
+%
+\begin{equation} \label{eq:5}
+	\rho_\mathrm{pre}(\tau,\beta) = e^{-iH_{MQ}\tau}\rho_\mathrm{eq}e^{iH_{MQ}\tau}
+\end{equation}
+%
+is the density matrix at the end of the preparation period,
+which can be defined from~Eqs.~(\ref{eq:2},\ref{eq:3}) and $\beta = \frac{\hbar \omega_0}{kT}$.
+
+It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{19}
+\begin{equation}
+    \label{eq:6}
+        \rho_\mathrm{pre}(\tau,\beta) = \sum_n \rho_{\mathrm{pre},n}(\tau,\beta),
+\end{equation}
+where $\rho_\mathrm{pre}(\tau,\beta)$ is the contribution to the density matrix $\rho_\mathrm{pre}(\tau,\beta)$ from the MQ coherence of the n--th order.
+Then the resulting signal $G(\tau,\phi)$ of the MQ NMR~\cite{9} can be rewritten as
+\begin{equation} \label{eq:7}
+    G(\tau, \phi) = \sum_n e^{in\phi}
+        Tr\left\{\rho_{\mathrm{pre},n}(\tau,\beta)
+        \rho_{\mathrm{pre},-n}(\tau,\beta) \right\},
+\end{equation}
+where we took into account that
+\begin{equation}
+    \label{eq:8}
+        [I_z, \rho_{\mathrm{pre},n}] = n \rho_{\mathrm{pre},n}
+\end{equation}
+The normalized intensities of the MQ NMR coherences can be determined as follows
+\begin{equation}
+    \label{eq:9}
+        J_n(\tau,\beta)= \frac{Tr\left\{\rho_{\mathrm{pre},n}(\tau,\beta)
+            \rho_{\mathrm{pre},-n}(\tau,\beta)\right\}}
+                {Tr(\rho^2_\mathrm{eq})}
+\end{equation}
+As was shown in~\cite{7},
+\begin{equation}
+    \label{eq:10}
+        Tr(\rho_\mathrm{eq}^2) = \frac{2^N ch^N (\beta)}{Z^2}
+\end{equation}
+It was also shown that
+\begin{equation}
+    \label{eq:11}
+        \sum_n J_n(\tau,\beta) = 1
+\end{equation}
+The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{20}
+\begin{equation}
+    \label{eq:12}
+        M_2(\tau,\beta) = -\frac{1}{G_2(\tau,0)}
+            \frac{d^2 G(t,\beta)}{dt^2}\bigg|
+        _{t=0}
+\end{equation}
+Using Eqs.~(\ref{eq:7},\ref{eq:8},\ref{eq:12}) one can obtain
+\begin{equation}
+    \label{eq:13}
+        M_2 (\tau,\beta) = \sum_n n^2 J_n(\tau,\beta)
+\end{equation}
+The low bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{6,8}.
+As a result, an analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of entangled spins at different temperatures~\cite{7}.
+In the following~Sec.~\ref{sec:3} we demonstrate that the Wigner--Yananse skew information is also connected with the second momentum $M_2(\tau,\beta)$ 
+and can be useful for an investigation of the many-spin entanglement.
+
+\section{The Wigner--Yanase skew information and MQ NMR}
 \label{sec:3}
+According definition~\cite{1,2} the Wigner--Yanase skew information
+\begin{equation}
+    \label{eq:14}
+        I_{WY}(\rho(\tau,\beta),I_z) = -\frac{1}{2}
+            Tr([\sqrt{\rho(\tau,\beta)},\sigma_z])^2 =
+                -2Tr([\sqrt{\rho(\tau,\beta)},I_z])^2,
+\end{equation}
+where the Pauli operator $\sigma_z=2I_z$.
+Introducing the evolution operator
+\begin{equation}
+    \label{eq:15}
+        V(\tau) = e^{iH_{MQ}\tau}
+\end{equation}
+and using Eq.~(\ref{eq:3}) one can write the density matrix $\rho(\tau,\beta)$ as follows:
+\begin{equation}
+    \label{eq:16}
+        \rho(\tau,\beta) = V^+(\tau) \frac{e^{\beta I_z}}{Z}V(\tau)
+\end{equation}
+Now we use te evident relationship:
+\begin{equation}
+    \label{eq:17}
+        \sqrt{\rho(\tau,\beta)} =
+            \sqrt{V^+(\tau)\frac{e^{\beta I_z}}{Z}V(\tau)} =
+                V^+(\tau) \frac{e^{\frac{\beta}{2}}I_z}{\sqrt{Z}}V(\tau).
+\end{equation}
+it can be proved by simple calculation:
+\begin{equation}
+    \label{eq:18}
+        \sqrt{\rho}\sqrt{\rho} =
+            V^+(\tau)\frac{e^\frac{\beta}{2}I_z}{\sqrt{Z}}
+                V(\tau)V^+(\tau)\frac{e^{\frac{\beta}{2}}I_z}{\sqrt{Z}}V(\tau) =
+            V^+(\tau)\frac{e^\beta I_z}{Z}V(\tau) =
+        \rho(\tau,\beta)
+\end{equation}
+%
+Then we have
+%
+\begin{equation} \label{eq:19}
+    \left[I_z,\sqrt{\rho(\tau,\beta)}\right] 
+    = \left[I_z, \sum_k \rho_k \left(\tau, \frac{\beta}{2}\right)\right] 
+    = \sum_k k\rho_k \left(\tau, \frac{\beta}{2}\right),
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:20}
+    Tr[I_z,\sqrt{\rho(\tau,\beta)}]^2 
+    = Tr\left\{\sum_{k,k'}kk'
+        \rho_k\left(\tau,\frac{\beta}{2}\right)
+        \rho_k\left(\tau,\frac{\beta}{2}\right) 
+    \right\}
+    = \sum_k k^2 J_k\left(\tau,\frac{\beta}{2}\right).
+\end{equation}
+%
+Finally, one can obtain that
+%
+\begin{equation} \label{eq:21}
+    I_{WY}\left(\rho(\tau, \beta), I_z\right)
+    = 2\sum_k k^2 J_k\left(\tau, \frac{\beta}{2}\right)
+    = 2M_2\left(\tau, \frac{\beta}{2}\right)
+\end{equation}
+%
+Thus, we obtain the important assertion.
+If the spin system is investigated with MQ NMR at temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the doubled second momentum of the distribution of the intensities of the MQ NMR coherences at temperature $2T \sim 2\beta^{-1}$ at any moment of the spin evolution.
 
-\section{A comparison of the many-spin entanglement obtained with the Wigner-Yanase information and the Fisher information}
+The Wagner-Yanase skew information is connected with the second moment of the distribution of the MQ NMR coherences analogously to the Fisher information.
+We compare these information the following Section~\ref{sec:4}.
+
+\section{A comparison of the many-spin entanglement obtained with the Wigner--Yanase information and the Fisher information}
 \label{sec:4}
+
+\begin{figure}
+	\includegraphics[width=0.95\linewidth]{entangled_spins_by_temp}
+	\caption{
+		The dependence of the number of the entangled spins on the inverse temperature $\beta = \frac{\pi \omega_0}{kT}$;
+		black circles - the results are obtained with the Fisher information;
+		open circles - results are obtained with the Wigner--Yanase information.
+	}
+	\label{fig:2}
+\end{figure}
+
+The Wigner--Yanase skew information $I_{WY}(\rho(\tau,\beta),I_z)$ and the Fisher information $I_F(\rho(\tau,\beta),I_z)$ can be used for an investigation of the many-spin entanglement.
+The informations are connected by the following restriction~\cite{3}
+%
+\begin{equation} \label{eq:22}
+    I_{WY}\left(\rho(\tau,\beta), I_z\right)
+    \leq I_F\left(\rho(\tau,\beta), I_z\right)
+    \leq 2I_{WY}\left(\rho(\tau,\beta), I_z\right).
+\end{equation}
+%
+The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strong by different.
+For the comparison we used the model~\cite{21} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
+This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{7}.
+
+We investigated the many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with 
+the Wigner--Yanase information $I_{WY}\left(\rho(\tau, \beta), I_z\right)$ 
+and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
+In Fig.~(\ref{fig:2})the dependence of the number of entangled spins on the inverse temperature is presented.
+Fig.~(\ref{fig:2}) demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
+
+The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{22}.
+Here the close results on the many--spin entanglement were obtained for both used informations for the system consisting of $6\div 12$ spins.
 
@@
 
+We studied the connection of the Wigner--Yanase skew information with the second moment of the distribution of the intensities of MQ coherences in the MQ NMR experiment.
+It was shown that the Wigner--Yanase skew information at temperature $T \sim \beta^{-1}$ equals to the double second momentum of the MQ NMR spectrum at temperature $2T \sim 2\beta^{-1}$.
+We compare also the results on the many--spin entanglement obtained with the Wigner--Yanase skew information and the Fisher information.
+
 \section{Acknowledgement}
 \label{sec:6}
+We acknowledge funding from the Ministry of Science and Higher Education of the Russian Federation (Grant No.~075-15-2020-779).
 
@@
 %%
- \bibliographystyle{elsarticle-num} 
- \bibliography{bibliography}
+% \bibliographystyle{elsarticle-num}
+% \bibliography{bibliography}
 
@@
 % \end{thebibliography}
+
+\begin{thebibliography}{20}
+\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, 49, 910-918 (1963)
+\bibitem{2} Z.Chen, Phys.Rev, A71, 052302 (2005)
+\bibitem{3} S.Luo, Proc.Amer. Math.Soc.132, No.885-890 (2003)
+\bibitem{4} G.Toth, I.Apellaniz, J. Phys. A47,424006 (2014)
+\bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. 90, 035005 (2018)
+\bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. 120, 040402 (2018)
+\bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A100,022330 (2019)
+\bibitem{8} D.Girolami, B.Yadin,Entropy 19,124 (2017)
+\bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. 83, 2015 (1985)
+\bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys. Rev. A94, 040302 (2010)
+\bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B27, A30 (2010)
+\bibitem{12} I.D. Leroux, M.H. Schleirer-Smith, V.Vuletii, Phys.Rev.Lett. 104,
+	073602 (2010)
+
+\bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev F94, 010102 (2016)
+\bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. 13,781 (2017)
+\bibitem{15} G.A.Bochkin, S.G.Vesil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. 51,667-678 (2020)
+\bibitem{16} E.B.Fel'dman, A.N. Pykov, A.I.Zenchuk, Philos. Trans. R. Soc. London A370, 4690 (2012)
+\bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokoovsky, Phys. Rev. A.78 042301 (2008)
+\bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
+\bibitem{19} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. 253, 27 (1996)
+\bibitem{20} A.Abragam, The Princioles of Nuclear Magnetism, Clarendon. Oxford. 1961
+\bibitem{21} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wn, Science 294, 1505 (2001)
+\bibitem{22} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)
+\end{thebibliography}
+
 \end{document}
 \endinput
-%%
-%% End of file `elsarticle-template-num.tex'.

### 2021-02-17 manuscript.tex
Fix bracket in math equation
Fix typos

@@
 A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with the dipole-dipole interactions in MQ NMR experiments in solids.
-It is shown that the Wigner--Yanase skew information at temperature is equal to the doubled second moment of the MQ NMR spectra at the temperature twice large and any evolution times.
+It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the doubled second moment of the MQ NMR spectra at the temperature twice large and any evolution times.
 A comparison of the many--spin entanglement obtained with the Wigner--Yanase information and the Fisher information is conducted.
@@
 in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
-Using the properties of the quantum Fisher Information one can obtain a number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
+Using the properties of the quantum Fisher information one can obtain a number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
 
 The Wigner--Yanase skew information~\cite{1,2,3} is also connected with the spectrum of MQ coherences.
-In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(S = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{9} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
+In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{9} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
 Using the properties of the Wigner--Yanase skew information one can investigate the many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{9}.
@@
 The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{9}.
-MQ NMR coherences are created by a periodic multipulse sequence, consisting of $I_x$-pulses, irradiating the system of the preparation period~\cite{9}.
+MQ NMR coherences are created by a periodic multipulse sequence, consisting of
+$\pm$-pulses, irradiating the system of the preparation period~\cite{9}.
 If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
@@
 \end{equation}
-where $Z=Tr \left\{e\frac{\hbar \omega_0}{kT}I_z \right\}$ is the partition function, $\hbar$ and $k$ are the Pauli and Boltzmann constants, $\omega_0$ is the Larmor frequency, $T$ is the temperature, and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis, which is directed along the strong external magnetic field.
+where $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ is the partition function, $\hbar$ and $k$ are the Pauli and Boltzmann constants, $\omega_0$ is the Larmor frequency, $T$ is the temperature, and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis, which is directed along the strong external magnetic field.
 
@@
 \end{equation}
-it can be proved by simple calculation:
+It can be proved by simple calculation:
 \begin{equation}
@@
 \begin{equation} \label{eq:20}
-    Tr[I_z,\sqrt{\rho(\tau,\beta)}]^2 
+	Tr\left[I_z,\sqrt{\rho(\tau,\beta)} \right]^2
 	= Tr\left\{\sum_{k,k'}kk'
 		\rho_k\left(\tau,\frac{\beta}{2}\right)
-        \rho_k\left(\tau,\frac{\beta}{2}\right) 
+		\rho_k'\left(\tau,\frac{\beta}{2}\right)
 	\right\}
@@
 Thus, we obtain the important assertion.
-If the spin system is investigated with MQ NMR at temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the doubled second momentum of the distribution of the intensities of the MQ NMR coherences at temperature $2T \sim 2\beta^{-1}$ at any moment of the spin evolution.
+If the spin system is investigated with MQ NMR at temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the double second momentum of the distribution of the intensities of the MQ NMR coherences at temperature $2T \sim 2\beta^{-1}$ at any moment of the spin evolution.
 
 The Wagner-Yanase skew information is connected with the second moment of the distribution of the MQ NMR coherences analogously to the Fisher information.
-We compare these information the following Section~\ref{sec:4}.
+We compare these informations the following Section~\ref{sec:4}.
 
@@
 		black circles - the results are obtained with the Fisher information;
-		open circles - results are obtained with the Wigner--Yanase information.
+		open circles - the results are obtained with the Wigner--Yanase information.
 	}
@@
 %
-The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strong by different.
 For the comparison we used the model~\cite{21} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
+The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strongly different.
 This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{7}.

### 2021-02-17 manuscript.tex
Add refferece and fix bibitem typos

@@
 If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
-MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$
+MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{19}
 %
@@
 
-It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{19}
+It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{20}
 \begin{equation}
@@
 \end{equation}
-The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{20}
+The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{21}
 \begin{equation}
@@
 %
-For the comparison we used the model~\cite{21} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
 The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strongly different.
+For the comparison we used the model~\cite{22} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
 This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{7}.
@@
 
-The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{22}.
-Here the close results on the many--spin entanglement were obtained for both used informations for the system consisting of $6\div 12$ spins.
+The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
+Here the close results on the many--spin entanglement were obtained for both used informations for the system consisting of $6\div 12$ spins~\cite{15}.
 
@@
 
-\bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev F94, 010102 (2016)
+\bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev A94, 010102 (2016)
 \bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. 13,781 (2017)
@@
 \bibitem{16} E.B.Fel'dman, A.N. Pykov, A.I.Zenchuk, Philos. Trans. R. Soc. London A370, 4690 (2012)
-\bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokoovsky, Phys. Rev. A.78 042301 (2008)
+\bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.78 042301 (2008)
 \bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
-\bibitem{19} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. 253, 27 (1996)
-\bibitem{20} A.Abragam, The Princioles of Nuclear Magnetism, Clarendon. Oxford. 1961
-\bibitem{21} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wn, Science 294, 1505 (2001)
-\bibitem{22} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)
+\bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.91, 597 (2000)
+\bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. 253, 27 (1996)
+\bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
+\bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wn, Science 294, 1505 (2001)
+\bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)
 \end{thebibliography}

### 2021-02-17 manuscript.tex
Fix typos

@@
 \author[icp]{S.~I.~Doronin}
-\author[icp]{E.~B.~Feldman}
+\author[icp]{E.~B.~Fel'dman}
 \author[icp,msu]{I.~D.~Lazarev}
@@
 A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with the dipole-dipole interactions in MQ NMR experiments in solids.
-It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the doubled second moment of the MQ NMR spectra at the temperature twice large and any evolution times.
+It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the double second moment of the MQ NMR spectrum at the temperature twice large and any evolution times.
 A comparison of the many--spin entanglement obtained with the Wigner--Yanase information and the Fisher information is conducted.
@@
 in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
-Using the properties of the quantum Fisher information one can obtain a number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
+Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
 
@@
 MQ NMR coherences are created by a periodic multipulse sequence, consisting of
-$\pm$-pulses, irradiating the system of the preparation period~\cite{9}.
+$\pm$x-pulses, irradiating the system of the preparation period~\cite{9}.
 If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
@@
 \end{equation}
-Now we use te evident relationship:
+Now we use the evident relationship:
 \begin{equation}
@@
 		\rho_k\left(\tau,\frac{\beta}{2}\right)
-		\rho_k'\left(\tau,\frac{\beta}{2}\right)
+		\rho_{k'}\left(\tau,\frac{\beta}{2}\right)
 	\right\}
@@
 
-The Wagner-Yanase skew information is connected with the second moment of the distribution of the MQ NMR coherences analogously to the Fisher information.
-We compare these informations the following Section~\ref{sec:4}.
+The Wigner-Yanase skew information is connected with the second moment of the distribution of the MQ NMR coherences analogously to the Fisher information.
+We compare these informations in the following Section~\ref{sec:4}.
 
@@
 \bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. 13,781 (2017)
-\bibitem{15} G.A.Bochkin, S.G.Vesil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. 51,667-678 (2020)
+\bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. 51,667-678 (2020)
 \bibitem{16} E.B.Fel'dman, A.N. Pykov, A.I.Zenchuk, Philos. Trans. R. Soc. London A370, 4690 (2012)
@@
 \bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
-\bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wn, Science 294, 1505 (2001)
+\bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science 294, 1505 (2001)
 \bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)

### 2021-02-17 manuscript.tex
Fix typos and reference styles

@@
 in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
-Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.
+Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6}
+and even to find the dependence of the number of entangled spins on temperature~\cite{8}.
 
@@
 %
-where $D_{jk}$ is the coupling constant between spins $j$ and $k$, and $I_{j} ^+ I_k ^-$ are the raising and lowering operators of spin $j$.
+where $D_{jk}$ is the coupling constant between spins $j$ and $k$,
+and $I_{j}^+, I_k ^-$ are the raising and lowering operators of spin $j$.
 On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
@@
 \begin{thebibliography}{20}
-\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, 49, 910-918 (1963)
-\bibitem{2} Z.Chen, Phys.Rev, A71, 052302 (2005)
-\bibitem{3} S.Luo, Proc.Amer. Math.Soc.132, No.885-890 (2003)
-\bibitem{4} G.Toth, I.Apellaniz, J. Phys. A47,424006 (2014)
-\bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. 90, 035005 (2018)
-\bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. 120, 040402 (2018)
-\bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A100,022330 (2019)
-\bibitem{8} D.Girolami, B.Yadin,Entropy 19,124 (2017)
-\bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. 83, 2015 (1985)
-\bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys. Rev. A94, 040302 (2010)
-\bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B27, A30 (2010)
-\bibitem{12} I.D. Leroux, M.H. Schleirer-Smith, V.Vuletii, Phys.Rev.Lett. 104,
-	073602 (2010)
-
-\bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev A94, 010102 (2016)
-\bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. 13,781 (2017)
-\bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. 51,667-678 (2020)
-\bibitem{16} E.B.Fel'dman, A.N. Pykov, A.I.Zenchuk, Philos. Trans. R. Soc. London A370, 4690 (2012)
-\bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.78 042301 (2008)
+	\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, \textbf{49}, 910-918 (1963)
+	\bibitem{2} Z.Chen, Phys.Rev.A. \textbf{71}, 052302 (2005)
+  \bibitem{3} S.Luo, Proc.Amer. Math.Soc. \textbf{132}, No.885-890 (2003)
+  \bibitem{4} G.Toth, I.Apellaniz, J. Phys. A. \textbf{47},424006 (2014)
+  \bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. \textbf{90}, 035005 (2018)
+  \bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. \textbf{120}, 040402 (2018)
+  \bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A. \textbf{100},022330 (2019)
+  \bibitem{8} D.Girolami, B.Yadin,Entropy \textbf{19},124 (2017)
+  \bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. \textbf{83}, 2015 (1985)
+  \bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A. \textbf{94}, 040302 (2010)
+  \bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B\textbf{27}, A30 (2010)
+  \bibitem{12} I.D. Leroux, M.H. Schleier-Smith, V.Vuletic, Phys.Rev.Lett. \textbf{104}, 073602 (2010)
+  \bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A. \textbf{94}, 010102 (2016)
+  \bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. \textbf{13} ,781 (2017)
+  \bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. \textbf{51},667-678 (2020)
+  \bibitem{16} E.B.Fel'dman, A.N. Pyrkov, A.I.Zenchuk, Philos. Trans. R. Soc. London A\textbf{370}, 4690 (2012)
+  \bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.\textbf{78} 042301 (2008)
   \bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
-\bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.91, 597 (2000)
-\bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. 253, 27 (1996)
+  \bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.\textbf{91}, 597 (2000)
+  \bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. \textbf{253}, 27 (1996)
   \bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
-\bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science 294, 1505 (2001)
-\bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)
+  \bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science \textbf{294}, 1505 (2001)
+  \bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. \textbf{319}, 106816 (2020)
 \end{thebibliography}

### 2021-02-19 manuscript.tex
Rename figure of entangled spins number in nanopore
Add figure of entangled spins number in zigzag

@@
 \begin{figure}
-	\includegraphics[width=0.95\linewidth]{entangled_spins_by_temp}
+	\includegraphics[width=0.95\linewidth]{nanopora_entangled_spins_by_temp}
 	\caption{
@@
 	\label{fig:2}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=0.95\linewidth]{zigzag_entangled_spins_by_temp}
+	\caption{
+		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $b$ (the inverse temperature) for zigzag chains consisting of six spins.
+	}
+	\label{fig:3}
 \end{figure}
@@
 and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
-In Fig.~(\ref{fig:2})the dependence of the number of entangled spins on the inverse temperature is presented.
+In Fig.~(\ref{fig:2}) the dependence of the number of entangled spins on the inverse temperature is presented.
 Fig.~(\ref{fig:2}) demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
@@
 The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
-Here the close results on the many--spin entanglement were obtained for both used informations for the system consisting of $6\div 12$ spins~\cite{15}.
+In Fig.~\ref{fig:3} the close results on the many--spin entanglement for both used informations for the system consisting of $6\div 12$ spins is presented.~\cite{15}.
 

### 2021-02-19 manuscript.tex
Fix typos

@@
 
-The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
-In Fig.~\ref{fig:3} the close results on the many--spin entanglement for both used informations for the system consisting of $6\div 12$ spins is presented.~\cite{15}.
+The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{15,23}.
+In Fig.~\ref{fig:3} the close results on the many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
 

### 2021-02-19 manuscript.tex
Add keywords and highlights

@@
 %%Research highlights
-%\begin{highlights}
-%\item Research highlight 1
-%\item Research highlight 2
-%\end{highlights}
+\begin{highlights}
+	\item multiple quantum NMR spectroscopy
+	\item connection of the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
+	\item the dependence of the number of entangled spins on temperature
+\end{highlights}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-multiple quantum (MQ) NMR \sep
+	many-spin entanglement \sep
+	Fisher information \sep
+	Wigner-Yanase skew information \sep
+	multiple quantum NMR \sep
+	multiple quantum coherences \sep
+	second moment \sep
+	temperature
 %% PACS codes here, in the form: \PACS code \sep code

### 2021-05-10 manuscript.tex
Fix title and highlights

@@
 
-\title{Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information}
+\title{Multiple quantum NMR in solids as a method of determination of Wigner--Yanase skew information}
 
@@
 	\item multiple quantum NMR spectroscopy
-	\item connection of the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
+	\item connection between the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
 	\item the dependence of the number of entangled spins on temperature

### 2021-05-10 manuscript.tex
Add ref about WY-information from Luo

@@
 \label{sec:1}
-The Wigner--Yanase skew information~\cite{1,2,3} together with the Fisher information~\cite{4,5} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{6,7}.
+The Wigner--Yanase skew information~\cite{1,2,3,4} together with the Fisher information~\cite{5,6} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{7,8}.
 Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
-In particular, it was shown~\cite{6,8} that a low bound on the quantum Fisher information~\cite{4,5} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
-As a result, the low bound on the quantum Fisher information can be found in MQ NMR experiments~\cite{9},
-in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
-Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6}
-and even to find the dependence of the number of entangled spins on temperature~\cite{8}.
+In particular, it was shown~\cite{7,9} that a low bound on the quantum Fisher information~\cite{5,6} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
+As a result, the low bound on the quantum Fisher information can be found in MQ~NMR experiments~\cite{10},
+in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{11,12,13,14,15}.
+Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{7}
+and even to find the dependence of the number of entangled spins on temperature~\cite{9}.
 
-The Wigner--Yanase skew information~\cite{1,2,3} is also connected with the spectrum of MQ coherences.
-In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{9} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
-Using the properties of the Wigner--Yanase skew information one can investigate the many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{9}.
+The Wigner--Yanase skew information~\cite{1,2,3,4} is also connected with the spectrum of MQ coherences.
+In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{10} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
+Using the properties of the Wigner--Yanase skew information one can investigate the many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{10}.
 
 The main aim of the present article is a development of the method of extracting the Wigner--Yanase skew information from the MQ NMR spectra.
-We also compare on the simple models~\cite{7,15} the many--spin entanglement obtained both with the Wigner--Yanase information and the Fisher information.
+We also compare on the simple models~\cite{8,16} the many--spin entanglement obtained both with the Wigner--Yanase information and the Fisher information.
 
@@
 The connection of the Wigner--Yanase skew information with the second moment of the MQ NMR spectrum is obtained in Sec.~\ref{sec:3}.
-A comparison of the many--spin entanglement obtained with Wigner--Yanase information and the Fisher information on the simple models~\cite{7,15} is conducted in Sec.~\ref{sec:4}.
+A comparison of the many--spin entanglement obtained with Wigner--Yanase information and the Fisher information on the simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
 We briefly discuss our results in the concluding Sec.~\ref{sec:5}.
@@
 
-MQ NMR methods are widely used for solving problems of quantum informatics~\cite{16,17}.
-The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{9}.
+MQ NMR methods are widely used for solving problems of quantum informatics~\cite{17,18}.
+The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{10}.
 MQ NMR coherences are created by a periodic multipulse sequence, consisting of
-$\pm$x-pulses, irradiating the system of the preparation period~\cite{9}.
-If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
-MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{19}
+$\pm$x-pulses, irradiating the system of the preparation period~\cite{10}.
+If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{19}
+MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{20}
 %
@@
 On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
-As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{9}.
+As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{10}.
 
-In order to investigate the MQ NMR dynamics of the system on the preparation period~\cite{9} one should find the density matrix $\rho(t)$ by solving the Liouville evolution equation~\cite{18}
+In order to investigate the MQ NMR dynamics of the system on the preparation period~\cite{10} one should find the density matrix $\rho(t)$ by solving the Liouville evolution equation~\cite{19}
 
@@
 
-Following the preparation evolution and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{9}, the resulting signal $G(\tau,\phi)$ stored as population information is
+Following the preparation evolution and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{10}, the resulting signal $G(\tau,\phi)$ stored as population information is
 %
@@
 
-It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{20}
+It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{21}
 \begin{equation}
@@
 where $\rho_\mathrm{pre}(\tau,\beta)$ is the contribution to the density matrix $\rho_\mathrm{pre}(\tau,\beta)$ from the MQ coherence of the n--th order.
-Then the resulting signal $G(\tau,\phi)$ of the MQ NMR~\cite{9} can be rewritten as
+Then the resulting signal $G(\tau,\phi)$ of the MQ NMR~\cite{10} can be rewritten as
 \begin{equation} \label{eq:7}
@@
 \end{equation}
-As was shown in~\cite{7},
+As was shown in~\cite{8},
 \begin{equation}
@@
 \end{equation}
-The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{21}
+The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{22}
 \begin{equation}
@@
 \end{equation}
-The low bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{6,8}.
-As a result, an analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of entangled spins at different temperatures~\cite{7}.
+The low bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
+As a result, an analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of entangled spins at different temperatures~\cite{8}.
 In the following~Sec.~\ref{sec:3} we demonstrate that the Wigner--Yananse skew information is also connected with the second momentum $M_2(\tau,\beta)$
@@
 \label{sec:3}
-According definition~\cite{1,2} the Wigner--Yanase skew information
+According definition~\cite{1,2,3} the Wigner--Yanase skew information
 \begin{equation}
@@
 The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strongly different.
-For the comparison we used the model~\cite{22} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
-This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{7}.
+For the comparison we used the model~\cite{23} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
+This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{8}.
 
@@
 
-The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{15,23}.
+The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{16,24}.
 In Fig.~\ref{fig:3} the close results on the many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
@@
 	\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, \textbf{49}, 910-918 (1963)
-	\bibitem{2} Z.Chen, Phys.Rev.A. \textbf{71}, 052302 (2005)
+	\bibitem{2} S.Luo, Phys.Rev.Lett. \textbf{91}, 180403 (2003)
   \bibitem{3} S.Luo, Proc.Amer. Math.Soc. \textbf{132}, No.885-890 (2003)
-  \bibitem{4} G.Toth, I.Apellaniz, J. Phys. A. \textbf{47},424006 (2014)
-  \bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. \textbf{90}, 035005 (2018)
-  \bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. \textbf{120}, 040402 (2018)
-  \bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A. \textbf{100},022330 (2019)
-  \bibitem{8} D.Girolami, B.Yadin,Entropy \textbf{19},124 (2017)
-  \bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. \textbf{83}, 2015 (1985)
-  \bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A. \textbf{94}, 040302 (2010)
-  \bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B\textbf{27}, A30 (2010)
-  \bibitem{12} I.D. Leroux, M.H. Schleier-Smith, V.Vuletic, Phys.Rev.Lett. \textbf{104}, 073602 (2010)
-  \bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A. \textbf{94}, 010102 (2016)
-  \bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. \textbf{13} ,781 (2017)
-  \bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. \textbf{51},667-678 (2020)
-  \bibitem{16} E.B.Fel'dman, A.N. Pyrkov, A.I.Zenchuk, Philos. Trans. R. Soc. London A\textbf{370}, 4690 (2012)
-  \bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.\textbf{78} 042301 (2008)
-  \bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
-  \bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.\textbf{91}, 597 (2000)
-  \bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. \textbf{253}, 27 (1996)
-  \bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
-  \bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science \textbf{294}, 1505 (2001)
-  \bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. \textbf{319}, 106816 (2020)
+	\bibitem{4} Z.Chen, Phys.Rev.A. \textbf{71}, 052302 (2005)
+  \bibitem{5} G.Toth, I.Apellaniz, J. Phys. A. \textbf{47},424006 (2014)
+  \bibitem{6} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. \textbf{90}, 035005 (2018)
+  \bibitem{7} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. \textbf{120}, 040402 (2018)
+  \bibitem{8} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A. \textbf{100},022330 (2019)
+  \bibitem{9} D.Girolami, B.Yadin,Entropy \textbf{19},124 (2017)
+  \bibitem{10} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. \textbf{83}, 2015 (1985)
+  \bibitem{11} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A. \textbf{94}, 040302 (2010)
+  \bibitem{12} F.M. Cucchietti, J.Opt.Soc. Am. B\textbf{27}, A30 (2010)
+  \bibitem{13} I.D. Leroux, M.H. Schleier-Smith, V.Vuletic, Phys.Rev.Lett. \textbf{104}, 073602 (2010)
+  \bibitem{14} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A. \textbf{94}, 010102 (2016)
+  \bibitem{15} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. \textbf{13} ,781 (2017)
+  \bibitem{16} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. \textbf{51},667-678 (2020)
+  \bibitem{17} E.B.Fel'dman, A.N. Pyrkov, A.I.Zenchuk, Philos. Trans. R. Soc. London A\textbf{370}, 4690 (2012)
+  \bibitem{18} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.\textbf{78} 042301 (2008)
+  \bibitem{19} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
+  \bibitem{20} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.\textbf{91}, 597 (2000)
+  \bibitem{21} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. \textbf{253}, 27 (1996)
+  \bibitem{22} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
+  \bibitem{23} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science \textbf{294}, 1505 (2001)
+  \bibitem{24} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. \textbf{319}, 106816 (2020)
 \end{thebibliography}

### 2021-05-10 manuscript.tex
Fix 'low bound'

@@
 Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
-In particular, it was shown~\cite{7,9} that a low bound on the quantum Fisher information~\cite{5,6} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
-As a result, the low bound on the quantum Fisher information can be found in MQ~NMR experiments~\cite{10},
+In particular, it was shown~\cite{7,9} that a lower bound on the quantum Fisher information~\cite{5,6} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
+As a result, the lower bound on the quantum Fisher information can be found in MQ~NMR experiments~\cite{10},
 in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{11,12,13,14,15}.
@@
 \end{equation}
-The low bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
+The lower bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
 As a result, an analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of entangled spins at different temperatures~\cite{8}.

### 2021-05-10 manuscript.tex
Fix typos

@@
 Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{7}
-and even to find the dependence of the number of entangled spins on temperature~\cite{9}.
+and even find the dependence of the number of entangled spins on temperature~\cite{9}.
 
@@
 The article is organized as follows.
-In Sec.~\ref{sec:2} the short introduction to the MQ NMR spectroscopy is given.
+In Sec.~\ref{sec:2} a short introduction to the MQ NMR spectroscopy is given.
 The connection of the Wigner--Yanase skew information with the second moment of the MQ NMR spectrum is obtained in Sec.~\ref{sec:3}.
-A comparison of the many--spin entanglement obtained with Wigner--Yanase information and the Fisher information on the simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
+A comparison of the many--spin entanglement obtained with the Wigner--Yanase and the Fisher information on the simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
 We briefly discuss our results in the concluding Sec.~\ref{sec:5}.
@@
 MQ NMR methods are widely used for solving problems of quantum informatics~\cite{17,18}.
-The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{10}.
+The MQ NMR experiment consists of four distinct periods of time as depicted in Fig.~\ref{fig:1}:
+preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{10}.
 MQ NMR coherences are created by a periodic multipulse sequence, consisting of
@@
 \end{equation}
-where $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ is the partition function, $\hbar$ and $k$ are the Pauli and Boltzmann constants, $\omega_0$ is the Larmor frequency, $T$ is the temperature, and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis, which is directed along the strong external magnetic field.
+where $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ is the partition function,
+$\hbar$ and $k$ are the Plank and Boltzmann constants respectively,
+$\omega_0$ is the Larmor frequency,
+$T$ is the temperature,
+and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis,
+which is directed along the strong external magnetic field.
 
@@
 
-It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau)$ in series as~\cite{21}
+It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau, \beta)$ in series as~\cite{21}
 \begin{equation}
@@
 \end{equation}
-where $\rho_\mathrm{pre}(\tau,\beta)$ is the contribution to the density matrix $\rho_\mathrm{pre}(\tau,\beta)$ from the MQ coherence of the n--th order.
+where $\rho_{\mathrm{pre}, n}(\tau,\beta)$ is the contribution to the density matrix $\rho_\mathrm{pre}(\tau,\beta)$ from the MQ coherence of the n--th order.
 Then the resulting signal $G(\tau,\phi)$ of the MQ NMR~\cite{10} can be rewritten as
@@
     \label{eq:10}
-        Tr(\rho_\mathrm{eq}^2) = \frac{2^N ch^N (\beta)}{Z^2}
+        Tr(\rho_\mathrm{eq}^2) = \frac{2^N ch^N (\beta)}{Z^2},
 \end{equation}
+where $N$ is the number of spins.
 It was also shown that
@@
 \label{sec:3}
-According definition~\cite{1,2,3} the Wigner--Yanase skew information
+The Wigner--Yanase skew information is defined as~\cite{1,2,3}
 \begin{equation}
@@
             \sqrt{V^+(\tau)\frac{e^{\beta I_z}}{Z}V(\tau)} =
-                V^+(\tau) \frac{e^{\frac{\beta}{2}}I_z}{\sqrt{Z}}V(\tau).
+                V^+(\tau) \frac{e^{\frac{\beta}{2}I_z}}{\sqrt{Z}}V(\tau).
 \end{equation}
@@
         \sqrt{\rho}\sqrt{\rho} =
-            V^+(\tau)\frac{e^\frac{\beta}{2}I_z}{\sqrt{Z}}
-                V(\tau)V^+(\tau)\frac{e^{\frac{\beta}{2}}I_z}{\sqrt{Z}}V(\tau) =
-            V^+(\tau)\frac{e^\beta I_z}{Z}V(\tau) =
+						V^+(\tau)\frac{e^{\frac{\beta}{2}I_z}}{\sqrt{Z}}
+                V(\tau)V^+(\tau)\frac{e^{\frac{\beta}{2}I_z}}{\sqrt{Z}}V(\tau) =
+						V^+(\tau)\frac{e^{\beta I_z}}{Z}V(\tau) =
         \rho(\tau,\beta)
@@
 and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
-In Fig.~(\ref{fig:2}) the dependence of the number of entangled spins on the inverse temperature is presented.
-Fig.~(\ref{fig:2}) demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
+In Fig.~\ref{fig:2} the dependence of the number of entangled spins on the inverse temperature is presented.
+Fig.~\ref{fig:2} demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
 

### 2021-05-10 manuscript.tex
Add 'N_ent' calculation details

@@
 The Wigner--Yanase skew information $I_{WY}(\rho(\tau,\beta),I_z)$ and the Fisher information $I_F(\rho(\tau,\beta),I_z)$ can be used for an investigation of the many-spin entanglement.
+Really, it is known~\cite{5,6} that if
+$I_{WY}\left( \rho(\tau, \beta), I_z \right)$
+or
+$I_{F}\left( \rho(\tau, \beta), I_z \right)$
+exceeds $mk^2 + (N - mk)^2$,
+where $k, m$ are integer and $m$ is the integer part of $N/k$,
+than we have $N_\mathrm{ent} = (k + 1) $~--~particle entangled spins in the system.
 The informations are connected by the following restriction~\cite{3}

### 2021-05-10 manuscript.tex
Fix punctuation

@@
 where $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ is the partition function,
-$\hbar$ and $k$ are the Plank and Boltzmann constants respectively,
+$\hbar$ and $k$ are the Plank and Boltzmann constants, respectively,
 $\omega_0$ is the Larmor frequency,

### 2021-05-11 manuscript.tex
Add missed citation
Fix bibliography style
Fix second moment equation (12)
Fix english grammar

@@
 %% Text of abstract
-A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with the dipole-dipole interactions in MQ NMR experiments in solids.
-It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the double second moment of the MQ NMR spectrum at the temperature twice large and any evolution times.
+A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with dipole-dipole interactions in MQ NMR experiments in solids.
+It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the double second moment of the MQ NMR spectrum at the double temperature for any evolution times.
 A comparison of the many--spin entanglement obtained with the Wigner--Yanase information and the Fisher information is conducted.
@@
 \label{sec:1}
-The Wigner--Yanase skew information~\cite{1,2,3,4} together with the Fisher information~\cite{5,6} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{7,8}.
-Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
+The Wigner--Yanase skew information~\cite{1,2,3,4} together with the Fisher information~\cite{5,6} allow the development of powerful methods for the investigation of entanglement, including many--particle entanglement~\cite{7,8}.
+Further investigations of many--particle entanglement require the development of corresponding experimental methods.
 In particular, it was shown~\cite{7,9} that a lower bound on the quantum Fisher information~\cite{5,6} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
 As a result, the lower bound on the quantum Fisher information can be found in MQ~NMR experiments~\cite{10},
-in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{11,12,13,14,15}.
-Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{7}
-and even find the dependence of the number of entangled spins on temperature~\cite{9}.
+in cold--atom experiments, including experiments with Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{11,12,13,14,15}.
+Using the properties of the quantum Fisher information one can obtain the number of the entangled particles (spins) in the system under consideration~\cite{7}
+and even find the dependence of the number of the entangled spins on the temperature~\cite{9}.
 
 The Wigner--Yanase skew information~\cite{1,2,3,4} is also connected with the spectrum of MQ coherences.
-In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in MQ NMR experiment~\cite{10} at the system temperature $T$ equals to the double second moment of the MQ NMR spectrum obtained at temperature $2T$.
-Using the properties of the Wigner--Yanase skew information one can investigate the many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{10}.
+In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in the MQ NMR experiment~\cite{10} at the system temperature $T$ equals the double second moment of the MQ NMR spectrum obtained at the temperature $2T$.
+Using the properties of the Wigner--Yanase skew information one can investigate many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{10}.
 
-The main aim of the present article is a development of the method of extracting the Wigner--Yanase skew information from the MQ NMR spectra.
+The main aim of the present article is the development of a method of extracting the Wigner--Yanase skew information from the MQ NMR spectra.
 We also compare on the simple models~\cite{8,16} the many--spin entanglement obtained both with the Wigner--Yanase information and the Fisher information.
@@
 The connection of the Wigner--Yanase skew information with the second moment of the MQ NMR spectrum is obtained in Sec.~\ref{sec:3}.
-A comparison of the many--spin entanglement obtained with the Wigner--Yanase and the Fisher information on the simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
-We briefly discuss our results in the concluding Sec.~\ref{sec:5}.
+A comparison of many--spin entanglement obtained with the Wigner--Yanase and the Fisher information on simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
+We briefly discuss our results in concluding Sec.~\ref{sec:5}.
 
@@
 $\pm$x-pulses, irradiating the system of the preparation period~\cite{10}.
-If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{19}
+If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{19} then
 MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{20}
@@
 and $I_{j}^+, I_k ^-$ are the raising and lowering operators of spin $j$.
-On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
+On the mixing period, the spin system is irradiated by the multiple pulse sequence with $\pm y$--pulses.
 As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{10}.
@@
 
-Following the preparation evolution and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{10}, the resulting signal $G(\tau,\phi)$ stored as population information is
+Following the preparation, evolution, and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{10}, the resulting signal $G(\tau,\phi)$ stored as population information is
 %
@@
 %
-is the density matrix at the end of the preparation period,
-which can be defined from~Eqs.~(\ref{eq:2},\ref{eq:3}) and $\beta = \frac{\hbar \omega_0}{kT}$.
+is the density matrix at the end of the preparation period.
+The density matrix can be obtained from~Eqs.~(\ref{eq:2},\ref{eq:3}) and $\beta = \frac{\hbar \omega_0}{kT}$.
 
@@
 \end{equation}
-where $N$ is the number of spins.
+where $N$ is the number of the spins.
 It was also shown that
@@
     \label{eq:12}
-        M_2(\tau,\beta) = -\frac{1}{G_2(\tau,0)}
-            \frac{d^2 G(t,\beta)}{dt^2}\bigg|
+        M_2(\tau,\beta) = -\frac{1}{G(\tau, \beta)}
+            \frac{d^2 G(\tau + t,\beta)}{dt^2}\bigg|
         _{t=0}
@@
 \end{equation}
-The lower bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
-As a result, an analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of entangled spins at different temperatures~\cite{8}.
-In the following~Sec.~\ref{sec:3} we demonstrate that the Wigner--Yananse skew information is also connected with the second momentum $M_2(\tau,\beta)$
-and can be useful for an investigation of the many-spin entanglement.
+A lower bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
+As a result, the analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of the entangled spins at different temperatures~\cite{8}.
+In the following~Sec.~\ref{sec:3} we demonstrate that the Wigner--Yananse skew information is also connected with the second moment $M_2(\tau,\beta)$
+and can be useful for the investigation of many-spin entanglement.
 
@@
 \label{sec:3}
-The Wigner--Yanase skew information is defined as~\cite{1,2,3}
+The Wigner--Yanase skew information is defined as~\cite{1,2,3,4}
 \begin{equation}
@@
 %
-Thus, we obtain the important assertion.
-If the spin system is investigated with MQ NMR at temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the double second momentum of the distribution of the intensities of the MQ NMR coherences at temperature $2T \sim 2\beta^{-1}$ at any moment of the spin evolution.
+Thus, we obtain an important observation.
+If the spin system is investigated with MQ NMR at the temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the double second moment of the distribution of the intensities of the MQ NMR coherences at the temperature $2T \sim 2\beta^{-1}$ at any time during the spin evolution.
 
@@
 
-\section{A comparison of the many-spin entanglement obtained with the Wigner--Yanase information and the Fisher information}
+\section{The comparison of the many-spin entanglement obtained with the Wigner--Yanase information and the Fisher information}
 \label{sec:4}
@@
 
-The Wigner--Yanase skew information $I_{WY}(\rho(\tau,\beta),I_z)$ and the Fisher information $I_F(\rho(\tau,\beta),I_z)$ can be used for an investigation of the many-spin entanglement.
-Really, it is known~\cite{5,6} that if
+The Wigner--Yanase skew information $I_{WY}(\rho(\tau,\beta),I_z)$ and the Fisher information $I_F(\rho(\tau,\beta),I_z)$ can be used for the investigation of the many-spin entanglement.
+Indeed, it is known~\cite{5,6} that if
 $I_{WY}\left( \rho(\tau, \beta), I_z \right)$
@@
 where $k, m$ are integer and $m$ is the integer part of $N/k$,
-than we have $N_\mathrm{ent} = (k + 1) $~--~particle entangled spins in the system.
+then we have $N_\mathrm{ent} = (k + 1) $~--~particle entangled spins in the system.
 The informations are connected by the following restriction~\cite{3}
@@
 %
-The restrictions (22) allow us to hope that the obtained results of the number of entangled spins are not strongly different.
+The restrictions (22) allow us to hope that the obtained results for the number of the entangled spins are not very different.
 For the comparison we used the model~\cite{23} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
-This model allows to investigate the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{8}.
+This model allows the investigation of the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{8}.
 
-We investigated the many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with
+We investigated many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with
 the Wigner--Yanase information $I_{WY}\left(\rho(\tau, \beta), I_z\right)$
 and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
-In Fig.~\ref{fig:2} the dependence of the number of entangled spins on the inverse temperature is presented.
+In Fig.~\ref{fig:2} the dependence of the number of the entangled spins on the inverse temperature is presented.
 Fig.~\ref{fig:2} demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
 
-The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{16,24}.
-In Fig.~\ref{fig:3} the close results on the many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
+An analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{16,24}.
+In Fig.~\ref{fig:3},  similar results on many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
 
@@
 We studied the connection of the Wigner--Yanase skew information with the second moment of the distribution of the intensities of MQ coherences in the MQ NMR experiment.
-It was shown that the Wigner--Yanase skew information at temperature $T \sim \beta^{-1}$ equals to the double second momentum of the MQ NMR spectrum at temperature $2T \sim 2\beta^{-1}$.
+It was shown that the Wigner--Yanase skew information at the temperature $T \sim \beta^{-1}$ equals the double second momentum of the MQ NMR spectrum at the temperature $2T \sim 2\beta^{-1}$.
 We compare also the results on the many--spin entanglement obtained with the Wigner--Yanase skew information and the Fisher information.
@@
 \begin{thebibliography}{20}
-	\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, \textbf{49}, 910-918 (1963)
+  \bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA \textbf{49}, 910-918 (1963)
   \bibitem{2} S.Luo, Phys.Rev.Lett. \textbf{91}, 180403 (2003)
   \bibitem{3} S.Luo, Proc.Amer. Math.Soc. \textbf{132}, No.885-890 (2003)
-	\bibitem{4} Z.Chen, Phys.Rev.A. \textbf{71}, 052302 (2005)
-  \bibitem{5} G.Toth, I.Apellaniz, J. Phys. A. \textbf{47},424006 (2014)
+  \bibitem{4} Z.Chen, Phys.Rev. A \textbf{71}, 052302 (2005)
+  \bibitem{5} G.Toth, I.Apellaniz, J. Phys. A \textbf{47},424006 (2014)
   \bibitem{6} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. \textbf{90}, 035005 (2018)
   \bibitem{7} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. \textbf{120}, 040402 (2018)
-  \bibitem{8} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A. \textbf{100},022330 (2019)
+  \bibitem{8} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A \textbf{100},022330 (2019)
   \bibitem{9} D.Girolami, B.Yadin,Entropy \textbf{19},124 (2017)
   \bibitem{10} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. \textbf{83}, 2015 (1985)
-  \bibitem{11} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A. \textbf{94}, 040302 (2010)
+  \bibitem{11} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A \textbf{94}, 040302 (2010)
   \bibitem{12} F.M. Cucchietti, J.Opt.Soc. Am. B\textbf{27}, A30 (2010)
   \bibitem{13} I.D. Leroux, M.H. Schleier-Smith, V.Vuletic, Phys.Rev.Lett. \textbf{104}, 073602 (2010)
-  \bibitem{14} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A. \textbf{94}, 010102 (2016)
+  \bibitem{14} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A \textbf{94}, 010102 (2016)
   \bibitem{15} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. \textbf{13} ,781 (2017)
@@
   \bibitem{17} E.B.Fel'dman, A.N. Pyrkov, A.I.Zenchuk, Philos. Trans. R. Soc. London A\textbf{370}, 4690 (2012)
-  \bibitem{18} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.\textbf{78} 042301 (2008)
+  \bibitem{18} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A \textbf{78} 042301 (2008)
   \bibitem{19} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.

### 2021-06-02 manuscript.tex
Fix 'b' to 'beta' in figures and captions

@@
 	\caption{
-		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $b$ (the inverse temperature) for zigzag chains consisting of six spins.
+		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $\beta$ (the inverse temperature) for zigzag chains consisting of six spins.
 	}

### 2021-12-18 manuscript.tex
Remove artifacts for arXiv
Translate to Russian lang

--- 2021-05-11 manuscript.tex
@@
 
-\journal{Physics Letters A}
+% \journal{Physics Letters A}
+
+\usepackage[utf8]{inputenc}
+\usepackage[T2A]{fontenc}
+\usepackage[russian]{babel}
 
@@
 
-\title{Multiple quantum NMR in solids as a method of determination of Wigner--Yanase skew information}
+\title{Многоквантовый ЯМР в твердых телах как метод определения информации Вигнера--Янасе}
 
@@
 
-\author[icp]{S.~I.~Doronin}
-\author[icp]{E.~B.~Fel'dman}
-\author[icp,msu]{I.~D.~Lazarev}
-\address[icp]{Institute of Problems of Chemical Physics of Russian Academy of Sciences, \\ Chernogolovka, Moscow Region, Russia 142432}
-\address[msu]{Faculty of Fundamental Physical-Chemical Engineering, Lomonosov Moscow State University, GSP-1, Moscow, Russia 119991}
+\author[icp]{C.~И.~Доронин}
+\author[icp]{Э.~Б.~Фельдман}
+\author[icp,msu]{И.~Д.~Лазарев}
+\address[icp]{Институт проблем химической физики Российской Академии Наук, \\ Черноголовка, Москва, Россия 142432} 
+\address[msu]{Факультет фундаментальной физико-химической инженерии. МГУ им. Ломоносова, GSP-1, Москва. Россия 119991}
 
@@
 %% Text of abstract
-A connection of the Wigner--Yanase skew information and multiple quantum (MQ) NMR coherences is considered at different temperatures and evolution times of nuclear spins with dipole-dipole interactions in MQ NMR experiments in solids.
-It is shown that the Wigner--Yanase skew information at temperature $T$ is equal to the double second moment of the MQ NMR spectrum at the double temperature for any evolution times.
-A comparison of the many--spin entanglement obtained with the Wigner--Yanase information and the Fisher information is conducted.
+В многоквантовом эксперименте  (МК) ЯМР в твердых телах рассматривается связь косой информации Вигнера--Янасе и  МК когерентностей ЯМР при разных температурах и временах эволюции ядерных спинов с диполь-дипольными взаимодействиями.
+Показано, что косая информация Вигнера--Янасе при температуре $T$ равна удвоенному второму моменту  спектра МК когерентностей ЯМР  при температуре $2T$ для любых времен эволюции.
+Проводится сравнение оценок многочастичной запутанности, полученной с помощью косой информации Вигнера--Янасе и информации Фишера.
 \end{abstract}
@@
 %%Research highlights
-\begin{highlights}
-	\item multiple quantum NMR spectroscopy
-	\item connection between the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
-	\item the dependence of the number of entangled spins on temperature
-\end{highlights}
+% \begin{highlights}
+% 	\item multiple quantum NMR spectroscopy
+% 	\item connection between the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
+% 	\item the dependence of the number of entangled spins on temperature
+% \end{highlights}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-	many-spin entanglement \sep
-	Fisher information \sep
-	Wigner-Yanase skew information \sep
-	multiple quantum NMR \sep
-	multiple quantum coherences \sep
-	second moment \sep
-	temperature
+    многочастичная запутанность \sep
+    информация Фишера \sep
+    косая информация Фишера \sep
+    многоквантовый ЯМР \sep
+    многоквантовые когерентности \sep
+    второй момент \sep
+    температура
+
 %% PACS codes here, in the form: \PACS code \sep code
@@
 
-\linenumbers
+% \linenumbers
 
@@
 \label{sec:1}
-The Wigner--Yanase skew information~\cite{1,2,3,4} together with the Fisher information~\cite{5,6} allow the development of powerful methods for the investigation of entanglement, including many--particle entanglement~\cite{7,8}.
-Further investigations of many--particle entanglement require the development of corresponding experimental methods.
-In particular, it was shown~\cite{7,9} that a lower bound on the quantum Fisher information~\cite{5,6} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
-As a result, the lower bound on the quantum Fisher information can be found in MQ~NMR experiments~\cite{10},
-in cold--atom experiments, including experiments with Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{11,12,13,14,15}.
-Using the properties of the quantum Fisher information one can obtain the number of the entangled particles (spins) in the system under consideration~\cite{7}
-and even find the dependence of the number of the entangled spins on the temperature~\cite{9}.
+Косая информация Вигнера--Янасе~\cite{1,2,3,4} так же, как и информация Фишера~\cite{5,6} позволяет разрабатывать методы для исследования многочастичной запутанности~\cite{7,8}. 
+Дальнейшее исследование многочастичной запутанности требует разработки соответствующих экспериментальных методов.
+В частности, было показано~\cite{7,9}, что нижняя граница квантовой информации Фишера~\cite{5,6} совпадает со вторым моментом спектра многоквантовых (МК) когерентностей. 
+В результате нижняя граница квантовой информации Фишера может быть найдена в МК эксперименте ЯМР~\cite{10},
+в экспериментах с холодными атомами, включая эксперименты с Бозе-Эйнштейновскими конденсатами, ионами в ловушках и др.~\cite{11,12,13,14,15}. 
+Используя свойства квантовой информации Фишера можно получить оценку снизу для числа запутанных частиц (спинов) в рассматриваемой системе~\cite{7} и даже найти зависимость этой оценки от температуры~\cite{9}.
 
-The Wigner--Yanase skew information~\cite{1,2,3,4} is also connected with the spectrum of MQ coherences.
-In particular, we demonstrate in the present article that the Wigner--Yanase skew information in a spin system $(s = 1/2)$ with the dipole--dipole interactions (DDI) in the MQ NMR experiment~\cite{10} at the system temperature $T$ equals the double second moment of the MQ NMR spectrum obtained at the temperature $2T$.
-Using the properties of the Wigner--Yanase skew information one can investigate many--spin entanglement on the basis of the MQ NMR spectroscopy~\cite{10}.
+Косая информация Вигнера-Янасе~\cite{1,2,3,4} также связана со спектром МК когерентностей. 
+В частности в данной работе мы демонстрируем, 
+что косая информация Вигнера--Янасе в системе спинов $(s = 1/2)$ c диполь-дипольным взаимодействием (ДДВ) в МК эксперименте ЯМР~\cite{10} с температурой системы $T$ 
+равна второму моменту спектра МК когерентностей ЯМР полученном при температуре $2T$. 
+Используя это свойство косой информации Вигнера--Янасе можно исследовать многочастичную запутанность на базе МК спектроскопии ЯМР~\cite{10}.
 
-The main aim of the present article is the development of a method of extracting the Wigner--Yanase skew information from the MQ NMR spectra.
-We also compare on the simple models~\cite{8,16} the many--spin entanglement obtained both with the Wigner--Yanase information and the Fisher information.
+Главная цель данной работы это разработка метода извлечения косой информации Вигнера--Янасе из спектра МК когерентностей ЯМР. 
+Мы также провели сравнение оценок многочастичной запутанности, полученных с помощью косой информации Вигнера--Янасе и информации Фишера для простой модели~\cite{8,16}.
 
-The article is organized as follows.
-In Sec.~\ref{sec:2} a short introduction to the MQ NMR spectroscopy is given.
-The connection of the Wigner--Yanase skew information with the second moment of the MQ NMR spectrum is obtained in Sec.~\ref{sec:3}.
-A comparison of many--spin entanglement obtained with the Wigner--Yanase and the Fisher information on simple models~\cite{8,16} is conducted in Sec.~\ref{sec:4}.
-We briefly discuss our results in concluding Sec.~\ref{sec:5}.
-
-\section{MQ NMR for solving problems of quantum informatics}
+\section{МК ЯМР для решения проблем квантовой информатики}
 \label{sec:2}
@@
 	\includegraphics[width=0.95\linewidth]{mq-experiment}
-	\caption{The basic scheme of the multiple quantum NMR experiment.}
+	\caption{Схема многоквантового эксперимента ЯМР.}
 	\label{fig:1}
@@
 
-MQ NMR methods are widely used for solving problems of quantum informatics~\cite{17,18}.
-The MQ NMR experiment consists of four distinct periods of time as depicted in Fig.~\ref{fig:1}:
-preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{10}.
-MQ NMR coherences are created by a periodic multipulse sequence, consisting of
-$\pm$x-pulses, irradiating the system of the preparation period~\cite{10}.
-If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{19} then
-MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{20}
+Методы МК ЯМР широко используются для решения проблем квантовой информатики~\cite{17,18}. 
+МК эксперимент ЯМР состоит из четырех уникальных периодов времени, изображенных на рисунке Рис.~\ref{fig:1}:
+подготовительный период $(\tau)$, период свободной эволюции $(t_1)$, период смешивания $(\tau)$ и период детектирования $(t_2)$~\cite{10}.
+МК когерентности ЯМР создаются периодической многоимпульсной последовательностью, 
+состоящей из $\pm$x-импульсов, которой облучают систему на подготовительном периоде~\cite{10}.
+Если период обращенной многоимпульсной последовательности значительно превышает локальное дипольное поле (в частотных единицах)~\cite{19}, 
+тогда МК динамика ЯМР может быть описана усредненным несекулярным двухквантовым Гамильтонианом~$H_{MQ}$~\cite{20}. 
 %
@@
 %
-where $D_{jk}$ is the coupling constant between spins $j$ and $k$,
-and $I_{j}^+, I_k ^-$ are the raising and lowering operators of spin $j$.
-On the mixing period, the spin system is irradiated by the multiple pulse sequence with $\pm y$--pulses.
-As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{10}.
+где $D_{jk}$ это константа диполь-дипольного взаимодействия между спинами $j$ и $k$,
+а $I_{j}^+, I_k ^-$ это повышающий и понижающий операторы для спина $j$.
+На периоде смешивания спиновая система облучается многоимпульсной последовательностью $\pm y$--импульсами. 
+В результате средний несекулярный двухквантовый Гамильтониан  на периоде смешивания равен~$(-H_{MQ})$~\cite{10}.
 
-In order to investigate the MQ NMR dynamics of the system on the preparation period~\cite{10} one should find the density matrix $\rho(t)$ by solving the Liouville evolution equation~\cite{19}
+В частности, для исследования МК динамики ЯМР для системы на подготовительном периоде~\cite{10} 
+следует найти матрицу плотности $\rho(t)$, решив эволюционное уравнение Лиувилля~\cite{19}.
 
@@
 \end{equation}
-with the initial thermodynamic equilibrium density matrix
+С начальным термодинамически равновесным состоянием
 \begin{equation}
@@
 \end{equation}
-where $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ is the partition function,
-$\hbar$ and $k$ are the Plank and Boltzmann constants, respectively,
-$\omega_0$ is the Larmor frequency,
-$T$ is the temperature,
-and $I_z$ is the operator of the projection of the total spin angular momentum on the $z$-axis,
-which is directed along the strong external magnetic field.
+где $Z=Tr \left\{exp\left(\frac{\hbar \omega_0}{kT}I_z\right) \right\}$ это статистическая сумма,
+$\hbar$ и $k$ это постоянные Планка и Больцмана соответственно,
+$\omega_0$ это Ларморовская частота, 
+$T$ - это температура
+и $I_z$ - это оператор проекции полного углового момента на ось~$z$,
+которая направлена вдоль сильного внешнего магнитного поля.
 
-Following the preparation, evolution, and mixing periods of the MQ NMR experiments and taking into account the phase increment $\phi$ of the radio-frequency pulses~\cite{10}, the resulting signal $G(\tau,\phi)$ stored as population information is
+Объединяя подготовительный период, период эволюции и период смешивания, 
+а также взяв во внимание инкремент фазы $\phi$ радиочастотных импульсов~\cite{10}, 
+результирующий сигнал $G(\tau,\phi)$ хранится в виде информации о населенности
 %
@@
 %
-where
+где
 %
@@
 %
-is the density matrix at the end of the preparation period.
-The density matrix can be obtained from~Eqs.~(\ref{eq:2},\ref{eq:3}) and $\beta = \frac{\hbar \omega_0}{kT}$.
+это матрица плотности в конце подготовительного периода. 
+Матрица плотности может быть получена из Ур.~(\ref{eq:2},\ref{eq:3}) и $\beta = \frac{\hbar \omega_0}{kT}$.
 
-It is convenient to expand the density matrix $\rho_\mathrm{pre}(\tau, \beta)$ in series as~\cite{21}
+Удобно представить матрицу плотности~$\rho_\mathrm{pre}(\tau, \beta)$ в виде ряда~\cite{21}
 \begin{equation}
@@
 \end{equation}
-where $\rho_{\mathrm{pre}, n}(\tau,\beta)$ is the contribution to the density matrix $\rho_\mathrm{pre}(\tau,\beta)$ from the MQ coherence of the n--th order.
-Then the resulting signal $G(\tau,\phi)$ of the MQ NMR~\cite{10} can be rewritten as
+где $\rho_{\mathrm{pre}, n}(\tau,\beta)$ это вклад МК когерентности n--ого порядка в матрицу плотности $\rho_\mathrm{pre}(\tau,\beta)$.  
+Тогда результирующий сигнал~$G(\tau,\phi)$ МК ЯМР~\cite{10} можно переписать в виде 
 \begin{equation} \label{eq:7}
@@
 \end{equation}
-where we took into account that
+где мы берем во внимание, что 
 \begin{equation}
@@
 \end{equation}
-The normalized intensities of the MQ NMR coherences can be determined as follows
+Нормализованные интенсивности МК когерентностей ЯМР могут быть определены как
 \begin{equation}
@@
 \end{equation}
-As was shown in~\cite{8},
+Как было паказано в~\cite{8},
 \begin{equation}
@@
 \end{equation}
-where $N$ is the number of the spins.
-It was also shown that
+где $N$ это число спинов в спиновой системе. 
+Также было показано, что 
 \begin{equation}
@@
 \end{equation}
-The second moment (dispersion) $M_2(\tau,\beta)$ of the distribution of the MQ NMR coherences $J_n (\tau,\beta)$ can be calculated from Eq.~(\ref{eq:7}) according to~\cite{22}
+Второй момент (дисперсия) $M_2(\tau,\beta)$ распределения интенсивностей МК когерентностей ЯМР  $J_n (\tau,\beta)$ может быть вычислен из Ур.~(\ref{eq:7}) согласно~\cite{22}.  
 \begin{equation}
@@
 \end{equation}
-Using Eqs.~(\ref{eq:7},\ref{eq:8},\ref{eq:12}) one can obtain
+Используя Ур.~(\ref{eq:7},\ref{eq:8},\ref{eq:12}) можно получить
 \begin{equation}
@@
 \end{equation}
-A lower bound on the quantum Fisher information coincides with the double second moment of Eq.~(\ref{eq:13})~\cite{7,9}.
-As a result, the analysis of the temperature dependence of the second moment $M_2(\tau,\beta)$ of the distribution of the intensities of the MQ NMR coherences allows us to obtain the number of the entangled spins at different temperatures~\cite{8}.
-In the following~Sec.~\ref{sec:3} we demonstrate that the Wigner--Yananse skew information is also connected with the second moment $M_2(\tau,\beta)$
-and can be useful for the investigation of many-spin entanglement.
+Нижняя граница квантовой информации Фишера совпадает со вторым моментом Eq.~(\ref{eq:13})~\cite{7,9}.
+В результате анализ температурной зависимости второго момента $M_2(\tau,\beta)$ распределения интенсивностей МК когерентностей ЯМР позволяет нам получить оценку числа запутанных спинов для разных температур~\cite{8}.
+В следующем разделе~\ref{sec:3} мы продемонстрируем, что косая информация Вигнера--Янасе
+также связана со вторым моментом $M_2(\tau,\beta)$ 
+и может быть полезна для исследования многочастичной запутанности.
 
-\section{The Wigner--Yanase skew information and MQ NMR}
+\section{Косая информация Вигнера--Янасе и МК ЯМР}
 \label{sec:3}
-The Wigner--Yanase skew information is defined as~\cite{1,2,3,4}
+Косая информация Вигнера--Янасе определяется как~\cite{1,2,3,4} 
 \begin{equation}
@@
 \end{equation}
-where the Pauli operator $\sigma_z=2I_z$.
-Introducing the evolution operator
+где~$\sigma_z=2I_z$~оператор Паули. 
+Введем оператор эволюции
 \begin{equation}
@@
 \end{equation}
-and using Eq.~(\ref{eq:3}) one can write the density matrix $\rho(\tau,\beta)$ as follows:
+и, используя Ур.~(\ref{eq:3}), можем записать матрицу плотности $\rho(\tau,\beta)$ как:
 \begin{equation}
@@
 \end{equation}
-Now we use the evident relationship:
+Теперь мы используем очевидное соотношение:
 \begin{equation}
@@
 \end{equation}
-It can be proved by simple calculation:
+Это можно доказать простым вычислением:
 \begin{equation}
@@
 %
-Then we have
+Теперь мы получаем
 %
@@
 %
-and
+и
 %
@@
 %
-Finally, one can obtain that
+В итоге мы получаем, что
 %
@@
 %
-Thus, we obtain an important observation.
-If the spin system is investigated with MQ NMR at the temperature $T\sim\beta^{-1}$ then the Wigner--Yanase skew information equals to the double second moment of the distribution of the intensities of the MQ NMR coherences at the temperature $2T \sim 2\beta^{-1}$ at any time during the spin evolution.
+Таким образом мы получили важное наблюдение.
+Если спиновая система исследуется с помощью МК ЯМР при температуре $T\sim\beta^{-1}$
+тогда косая информация Вигнера--Янасе равна второму моменту распределения интенсивности МК когерентностей ЯМР при температуре $2T \sim 2\beta^{-1}$ для любого времени эволюции.
 
-The Wigner-Yanase skew information is connected with the second moment of the distribution of the MQ NMR coherences analogously to the Fisher information.
-We compare these informations in the following Section~\ref{sec:4}.
+Косая информация Вигнера--Янасе связана со вторым моментом распределения интенсивности МК когерентностей ЯМР так же как и информация Фишера.
+Сравнение оценок многочастичной запутанности на основе этих информаций приведено в следующей секции~\ref{sec:4}.
 
-\section{The comparison of the many-spin entanglement obtained with the Wigner--Yanase information and the Fisher information}
+\section{Сравнение оценок многочастичной запутанности, полученной с помощью косой информации Вигнера--Янасе и информации Фишера}
 \label{sec:4}
@@
 	\caption{
-		The dependence of the number of the entangled spins on the inverse temperature $\beta = \frac{\pi \omega_0}{kT}$;
-		black circles - the results are obtained with the Fisher information;
-		open circles - the results are obtained with the Wigner--Yanase information.
+	    Зависимость $N_\mathrm{ent}$ оценки снизу для числа запутанных спинов от обратной температуры $\beta = \frac{\pi \omega_0}{kT}$ для системы эквивалентных спинов;
+	    черные точки --- результаты полученные из информации Фишера;
+	    белые точки --- результаты полученные из косой информации Вигнера--Янасе;
 	}
@@
 	\caption{
-		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $b$ (the inverse temperature) for zigzag chains consisting of six spins.
+	    Зависимость $N_\mathrm{ent}$ оценки снизу для числа запутанных спинов от обратной температуры $\beta = \frac{\pi \omega_0}{kT}$ для альтерированной  цепочки;
+	    черные точки --- результаты полученные из информации Фишера;
+	    белые точки --- результаты полученные из косой информации Вигнера--Янасе;
 	}
@@
 
-The Wigner--Yanase skew information $I_{WY}(\rho(\tau,\beta),I_z)$ and the Fisher information $I_F(\rho(\tau,\beta),I_z)$ can be used for the investigation of the many-spin entanglement.
-Indeed, it is known~\cite{5,6} that if
+Косая информация Фишера  $I_{WY}(\rho(\tau,\beta),I_z)$ и информация Фишера $I_F(\rho(\tau,\beta),I_z)$
+могут быть использованы для исследования многочастичной запутанности. 
+Известно~\cite{5,6}, что если
 $I_{WY}\left( \rho(\tau, \beta), I_z \right)$
-or
+или
 $I_{F}\left( \rho(\tau, \beta), I_z \right)$
-exceeds $mk^2 + (N - mk)^2$,
-where $k, m$ are integer and $m$ is the integer part of $N/k$,
-then we have $N_\mathrm{ent} = (k + 1) $~--~particle entangled spins in the system.
-The informations are connected by the following restriction~\cite{3}
+превышает $mk^2 + (N - mk)^2$,
+где $k, m$ целые, а $m$ это целая часть от $N/k$,
+тогда состояние содержит несепарабельную подсистему с $N_\mathrm{ent} = (k + 1) $ частицами. 
+Информации связанны следующим неравенством~\cite{3}:
 %
@@
 %
-The restrictions (22) allow us to hope that the obtained results for the number of the entangled spins are not very different.
-For the comparison we used the model~\cite{23} of a nonspherical nanopore filled with a gas of spin-carrying atoms (for example, xenon) or molecules in a strong external magnetic field.
-This model allows the investigation of the many-spin entanglement in the spin system consisting of hundreds of nuclear spins~\cite{8}.
+Данное неравенство~(\ref{eq:22}) позволяет нам надеяться, что результаты для оценки количества запутанных спинов не будут значительно отличаться. 
+Для сравнения мы используем модель~\cite{23} несферической нанопоры, заполненной газом спин несущих атомов (например, ксенон) или молекул в сильном внешнем магнитном поле. 
+Эта модель позволяет исследовать многочастичную запутанность в спиновой системе, состоящей из сотни ядерных спинов~\cite{8}.
 
-We investigated many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with
-the Wigner--Yanase information $I_{WY}\left(\rho(\tau, \beta), I_z\right)$
-and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
-In Fig.~\ref{fig:2} the dependence of the number of the entangled spins on the inverse temperature is presented.
-Fig.~\ref{fig:2} demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.
+Мы исследуем многочастичную запутанность в спиновой системе, состоящую из 201 спина
+в нанопоре.
+На Рис.~\ref{fig:2} изображена зависимость $N_\mathrm{ent}$ оценки снизу для числа запутанных спинов от обратной температуры.
+Число запутанных спинов растет с понижением температуры для обеих информаций.
 
-An analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{16,24}.
-In Fig.~\ref{fig:3},  similar results on many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
+Также по аналогии было проведено исследование модели альтерированной цепочки протонов в монокристалле гамбергита~\cite{16,24}.
+На Рис.~\ref{fig:3} изображен схожее поведение многочастичной запутанности для цепочки из 6 спинов для обеих информаций.
 
-\section{Conclusion}
+\section{Выводы}
 \label{sec:5}
 
-We studied the connection of the Wigner--Yanase skew information with the second moment of the distribution of the intensities of MQ coherences in the MQ NMR experiment.
-It was shown that the Wigner--Yanase skew information at the temperature $T \sim \beta^{-1}$ equals the double second momentum of the MQ NMR spectrum at the temperature $2T \sim 2\beta^{-1}$.
-We compare also the results on the many--spin entanglement obtained with the Wigner--Yanase skew information and the Fisher information.
+Мы изучили связь косой информации Вигнера--Янасе со вторым моментом распределения интенсивностей МК когерентностей ЯМР в МК эксперименте ЯМР. 
+Было параказно, что косая информация Вигнера--Янасе при температуре $T \sim \beta^{-1}$ равна 
+удвоенному второму моменту МК ЯМР спектра при температуре $2T \sim 2\beta^{-1}$.
+Было проведено сравнение оценок количества запутанных спинов полученных с помощью косой информации Вигнера--Янасе и информации Фишера.
 
@@
 \label{sec:6}
-We acknowledge funding from the Ministry of Science and Higher Education of the Russian Federation (Grant No.~075-15-2020-779).
+Мы благодарим фонд Министерства науки и высшего образования РФ (Grant No.~075-15-2020-779)
 
